Death by Dropdown?<br>Engineer Insightful Shiny Apps<br>with Behavioral Science

### 2025-09-12 conference-materials/2025_posit-conf/draft.qmd
Enhance slide layout and styling
- Adjusted overlay text box position and spacing for improved visibility.
- Converted bullet-pointed research details into paragraph format to better match visual storytelling.
- Introduced stacked image transitions in the Paradox of Choice example for smoother visual flow.
- Applied consistent heading color styles to emphasize key concepts (e.g., BID Framework, Road Trip, R Package).
- Updated custom CSS to increase left margin on 70% width columns in slides with dark backgrounds for improved readability.
- Added new blurred image (`jam-study-blur.png`) to sup

## {background-image="img/ui-before.png" background-size="contain" background-position="right" background-color="#2c3e50"}

::: {.text-box-overlay-dark .absolute left="-150" bottom="165" .fragment}
### Real client. Real dashboard. Real problems.

@@

::: { style="margin-top: var(--space-7);"}
:::: {.columns}
::: {.column width="45%" .fragment}
### Classic Example: The Paradox of Choice {style="color: var(--coral-light) !important;"}

::: {.text-large}
- **Researchers**: Sheena Iyengar & Mark Lepper
- **Setting**: Upscale grocery store sampling booth
- **Design**: 24 jams vs. 6 jams display
- **Key Finding**: More choice attracted browsers but paralyzed buyers
:::
:::

::: {.column width="45%" .fragment}
### Study Results {style="color: var(--teal-light) !important;"}

![](img/jam-study.png){width="100%" style="border-radius: 8px; box-shadow: 0 4px 12px rgba(0,0,0,0.15);"}
:::
::::
:::

::: {.fragment .center style="font-weight: 600; margin-top: 30px;"}
**10x higher conversion with fewer options**
:::

::: {.notes}
- 1 minute
- Behavioral science studies how people think, feel, and act...often in the context of decision making
- Surprise...we're not rational...but we are still predictable and fairly consistent when we pay attention to the right drivers
- Let me show you a classic example that mirrors our dashboard problem...Sheena Iyengar & Mark Lepper’s famous jam study at Columbia
- They studied people in the field at a fancy grocery store...think Whole Foods or Trader Joe's
- These shoppers walked by a display stand with either 24 jams...(extensive choice condition)...or 6 jams (limited choice condition)
- More choice drew people in...60% stopped at the big display vs. 40% at the small one
- But fewer choices drove action...nearly 30% bought jam after the 6-jam booth, compared to only 3% after the 24-jam booth
- More choice attracted browsers...but paralyzed buyers
- So what do we learn from this?
    - Too many options look appealing but kill follow-through...exactly what happens with dashboards overloaded with filters
:::

@@

:::: {.columns}
::: {.column width="30%"}
### Think of it like a road trip

@@

::: {.column width="70%" .fragment}
### The BID Framework

@@

![](img/bid-framework.png){style="box-shadow: none !important; width: 100%;"}
:::
::::

@@

:::: {.columns}
::: {.column width="45%" .text-large}
An R package that:

@@

::: {.column width="45%" .fragment style="margin-top: 150px;"}
### *Your behavioral scientist in the console* {style="text-align: center !important; color: var(--teal-light) !important;"}
:::
::::

>>>>

## {background-image="img/ui-before.png" background-size="contain" background-color="#2c3e50"}

::: {.text-box-overlay-dark .absolute left="-200" bottom="100" .fragment}
### Real client. Real dashboard. Real problems.

@@

::: { style="margin-top: var(--space-7);"}
:::: {.columns .fragment}

### Classic Example: The Paradox of Choice {style="text-align: center; color: var(--coral-light) !important;"}

::: {.column width="45%" .fragment}

::: {.text-large}
**Researchers**: Sheena Iyengar & Mark Lepper

**Setting**: Upscale grocery store sampling booth

**Design**: 24 jams vs. 6 jams display
:::
:::

::: {.column width="45%"}
::: {.r-stack}
![](img/jam-study-blur.png){.fragment width="100%" style="border-radius: 8px; box-shadow: 0 4px 12px rgba(0,0,0,0.15);"}

![](img/jam-study.png){.fragment width="100%" style="border-radius: 8px; box-shadow: 0 4px 12px rgba(0,0,0,0.15);"}
:::
:::

::::
:::

::: {.fragment .center style="margin-top: 30px;"}
### **10x higher conversion with fewer options** {style="color: var(--teal-light) !important;"}
:::

::: {.notes}
- 1 minute
- Behavioral science studies how people think, feel, and act...often in the context of decision making
- Surprise...we're not rational...but we are still predictable and fairly consistent when we pay attention to the right drivers
- Let me show you a classic example that mirrors our dashboard problem...Sheena Iyengar & Mark Lepper's famous jam study at Columbia
- They studied people in the field at a fancy grocery store...think Whole Foods or Trader Joe's
- These shoppers walked by a display stand with either 24 jams...(extensive choice condition)...or 6 jams (limited choice condition)
- More choice drew people in...60% stopped at the big display vs. 40% at the small one
- But fewer choices drove action...nearly 30% bought jam after the 6-jam booth, compared to only 3% after the 24-jam booth
- More choice attracted browsers...but paralyzed buyers
- So what do we learn from this?
    - Too many options look appealing but kill follow-through...exactly what happens with dashboards overloaded with filters
:::

@@

:::: {.columns}
::: {.column width="30%"}
### Think of it like a road trip {style="color: var(--coral-light) !important;"}

@@

::: {.column width="70%" .fragment}
### The BID Framework {style="color: var(--indigo-light) !important;"}

@@

![](img/bid-framework.png){style="box-shadow: none !important; margin-left: 10%"}
:::
::::

@@

:::: {.columns}
::: {.column width="45%" .text-large}
### An R package that: {style="color: var(--teal-light) !important;"}

@@

::: {.column width="45%" .fragment style="margin-top: 150px;"}
### *Your behavioral scientist in the console* {style="text-align: center !important; color: var(--indigo-light) !important;"}
:::
::::
